Douglas-Complex Fire PM2.5

### 2018-09-17 r_scripts/analysis/wfs_exposure_figures.Rmd
Updated scripts for paper.

# estimate county smoke 
county_smk_count <- county_pm_df %>% 
  # binary smoke variable at >10 ug/m^3
  mutate(gwr_smk10 = ifelse(geo_smk_pm >= 10, 1, 0)) %>% 
  group_by(county) %>% 
  summarise(smk_day10 = sum(gwr_smk10)) %>% 
  # lower case county name and remove "." to match spatial df
  mutate(subregion = tolower(stringr::str_replace(county, "[.]", " ")))

@@

We summarize smoke exposure two ways: as a count of days where smoke PM~2.5~ is > 10 ug/m^3 (to increase the specificity to identify areas impacted by smoke) at the county level, and time-series of county-population weighted PM~2.5~ over May to October 2013.

### Number of days in Oregon where smoke PM~2.5~ exceeded 10 ug/m^3.

```{r smoke days map}
smoke_map <- ggplot(or_county_spatial_df, aes(x=long,y=lat, group=group)) +
  # fill with number of smoke days
  geom_polygon(aes(fill =smk_day10)) +
  scale_fill_gradient2(expression("Smoke Days > 10 µg/m"^3),
                       low = "white", mid= "#00dbde", high="#6a3093", 
                       midpoint = 15,
    guide = guide_colorbar(direction="horizontal", title.position = "top",
                          title.hjust = 0.5, barwidth = 20)) +
  # add county path on top
  geom_path(colour="#4ac29a") +
  # adding fire locations in
  geom_point(data=fire_locations, 
             aes(x=lon, y=lat, size = sqrt(area/2)), 
             color = "red", shape = 17, alpha = 0.7, 
             show.legend = F, inherit.aes = FALSE) +
  # add county text 
  geom_text(data = county_text, 
            aes(x=long, y=lat, label = county, group="county"), 
            color = "#33001b", size = 2.5, inherit.aes = F) +
  # add metropolitan
  geom_point(data = msa_location, 
    aes(x=Longitude, y=Latitude), 
    size = 1, color = '#ff0084', shape = 19, alpha = 0.7,
    show.legend = F, inherit.aes = FALSE) +
  # add metro text
  geom_text(data = msa_text, 
    aes(x=Longitude + c(0.15,0.1,0.1,-0.05,0.2,0.1), 
        y=Latitude + c(0.2,0.1,0.1,-0.1,0.1,0.1), 
        label = metro_area, group="MSA"), 
    color = "#ff0084", size = 3) +
  xlab("Longitude") +
  ylab("Latitude") +
  theme(panel.background = element_rect(fill = 'white', colour = 'black'),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.background = element_rect(colour=NA, fill=NA),
        legend.position = "bottom")

>>>>

# estimate county smoke 
county_smk_count <- county_pm_df %>% 
  # binary smoke variable at >10 ug/m^3
  mutate(gwr_smk10 = ifelse(geo_smk_pm >= 10, 1, 0),
         gwr_smk15 = ifelse(geo_smk_pm >= 15, 1, 0)) %>% 
  group_by(county) %>% 
  summarise(smk_day10 = sum(gwr_smk10), smk_day15 = sum(gwr_smk15)) %>% 
  # lower case county name and remove "." to match spatial df
  mutate(subregion = tolower(stringr::str_replace(county, "[.]", " ")))

@@

We summarize smoke exposure two ways: as a count of days where smoke PM~2.5~ is > 15 ug/m^3 (to increase the specificity to identify areas impacted by smoke) at the county level, and time-series of county-population weighted PM~2.5~ over May to October 2013.

### Number of days in Oregon where smoke PM~2.5~ exceeded 15 ug/m^3.

```{r smoke days map}
smoke_map <- ggplot(or_county_spatial_df, aes(x=long,y=lat, group=group)) +
  # fill with number of smoke days
  geom_polygon(aes(fill = smk_day15)) +
  scale_fill_gradient2(expression("Smoke Days > 15 µg/m"^3),
                       low = "white", mid= "#00dbde", high="#6a3093", 
                       midpoint = 10,
    guide = guide_colorbar(direction = "horizontal", title.position = "top",
                          title.vjust = 2, title.hjust = 0.5, barwidth = 15)) +
  # add county path on top
  geom_path(colour="#4ac29a") +
  # adding fire locations in
  geom_point(data=fire_locations, 
             aes(x=lon, y=lat, size = sqrt(area/2)), 
             color = "red", shape = 17, alpha = 0.7, 
             show.legend = T, inherit.aes = FALSE) +
  # legend for firsts for fires
  scale_size('Wildfire Acres Burned', breaks = c(0.8, 1, 1.6), 
             labels = c(1600, 4000, 26000),
             guide = guide_legend(title.position = "top", direction = "horizontal",
                                  title.hjust = 0.5, barwidth = 10)) +
  # add county text 
  geom_text(data = county_text, 
            aes(x=long, y=lat, label = county, group="county"), 
            color = "#33001b", size = 2.5, inherit.aes = F) +
  # add metropolitan
  geom_point(data = msa_location, 
    aes(x=Longitude, y=Latitude), 
    size = 1, color = '#ff0084', shape = 19, alpha = 0.7, 
    show.legend = F, inherit.aes = FALSE) +
  # add metro text
  geom_text(data = msa_text, 
    aes(x=Longitude + c(0.15,0.1,0.1,-0.05,0.2,0.1), 
        y=Latitude + c(0.2,0.1,0.1,-0.1,0.1,0.1), 
        label = metro_area, group="MSA"), 
    color = "#ff0084", size = 3) +
  xlab("Longitude") +
  ylab("Latitude") +
  theme(panel.background = element_rect(fill = 'white', colour = 'black'),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.background = element_rect(colour=NA, fill=NA),
        legend.position = "bottom",
        legend.key = element_rect(fill = NA, colour = NA, size = 0.25))
